---
title: "Introduction to linreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab04)
```

## Introduction

The function linreg() implements linear regression using QR decomposition.
It returns an object of class "linreg" that contains regression results and provides methods for:

printing the model,

extracting coefficients, residuals, and fitted values,

summarizing results (with SE, t-values, and p-values),

plotting diagnostic graphs.

In this vignette we demonstrate how to use linreg with the iris and faithful datasets.

---

## Example 1: Iris dataset

We model **Sepal.Length** as a function of **Sepal.Width** and **Petal.Length**.

```{r}
data(iris)

# Fit the model
fit <- linreg(Sepal.Length ~ Sepal.Width + Petal.Length, data = iris)
```

Printing the model
```{r}
fit$print()
```

Plot residuals
```{r}
fit$plot()
```

Get the vector of residuals
```{r}
head(fit$resid(), 10)   # first 10 residuals
```

Get the vector of predicted values
```{r}
head(fit$pred(), 10)    # first 10 predicted values
```

Get the coefficients as a vector
```{r}
fit$coef()
```

Get the summary of the model
```{r}
fit$summary()
```


## Example 2: Faithful dataset

We now model eruption duration (**eruptions**) as a function of waiting time (**waiting**).
```{r}
data(faithful)

fit2 <- linreg(eruptions ~ waiting, data = faithful)
fit2
```

Summary and plots
```{r}
fit2$summary()
fit2$plot()
```



## Conclusion

The linreg function provides a simple implementation of linear regression with
methods for inspecting coefficients, fitted values, residuals, statistical inference,
and diagnostic plots, similar to the built–in lm() function in R.
